Syntax and Semantics of Abstract Binding Trees

### 2015-12-02 paper.tex
finish up operator interpretation example
Define sheafification

Going forward, we will write $\SCtxSite$ for the Grothendieck site
$\Pair{\OpCat{\left(\SCtx\right)}}{A}$, where $A$ is the atomic coverage (sc.\
every non-empty family covers).

@@

For any Grothendieck site $\Match{\mathfrak{S}}{\Pair{\mathcal{C}}{J}}$, the
inclusion $\Of{\iota}{\Sheaves{\mathfrak{S}}\ra\Presheaves{\mathcal{C}}}$ of
sheaves into presheaves has a left adjoint
$\IMode{\Sheafify{(-)}}\dashv\IMode{\iota}$, which takes any presheaf
$\Of{X}{\Presheaves{\mathcal{C}}}$ to a unique sheaf
$\Of{\Sheafify{X}}{\Sheaves{\mathfrak{S}}}$, called the \emph{sheafification}
of $X$.

@@

These rules correspond to the following family of sheaves:
\begin{align*}
  \ADefine{
    \Operators_{
      \MkArity{
        \MkValence{}{}{\SortExp},
        \MkValence{\SortExp}{}{\SortExp}
      }{
        \SortExp
      }
    }
  }{
    \mathbb{1}
  }\\
  \ADefine{
    \Operators_{
      \MkArity{}{\SortExp}
    }
  }{
    \mathbf{S}_\SortExp
  }
\end{align*}

>>>>

Going forward, we will write $\SCtxSite$ for the Grothendieck site
$\Pair{\OpCat{\left(\SCtx\right)}}{J_\mathsf{atm}}$, where $J_\mathsf{atm}$
is the atomic coverage (sc.\ every non-empty family covers).

@@

For any Grothendieck site $\Match{\mathfrak{S}}{\Pair{\mathcal{C}}{J}}$, the
inclusion $\Of{\iota}{\Sheaves{\mathfrak{S}}\ra\Presheaves{\mathcal{C}}}$ of
sheaves into presheaves has a left adjoint
$\IMode{\Sheafify{(-)}}\dashv\IMode{\iota}$, which takes any presheaf
$\Of{X}{\Presheaves{\mathcal{C}}}$ to a unique sheaf
$\Of{\Sheafify{X}}{\Sheaves{\mathfrak{S}}}$, called the \emph{sheafification}
of $X$. Sheafification is the twice-iterated application of the
\emph{+-construction} $X^+$, which turns a presheaf into a separated presheaf,
and a separated presheaf into a sheaf:
\begin{align*}
  \ADefine{
    X^+(C)
  }{
    \int^{S\in J(C)}
    \Hom{\Presheaves{\mathcal{C}}}{S}{X}
  }\\
  \ADefine{
    \Sheafify{X}
  }{
    X^{++}
  }
\end{align*}

We also have a canonical map $\Of{\eta}{X\ra X^+}$, defined
using the maximal sieve $\Define{t_C}{\Yoneda{C}}$:
\[
  \HypJ{
    \Define{\eta_C(m)}{
      \Pair{t_C}{
        X(-)(m)
      }
    }
  }{
    \Member{m}{X(C)}
  }
\]

@@

These rules correspond to the following family of sheaves:
\begin{align*}
  \ADefine{
    \Operators_{
      \MkArity{
        \MkValence{}{}{\SortExp},
        \MkValence{\SortExp}{}{\SortExp}
      }{
        \SortExp
      }
    }
  }{
    \mathbb{1}
  }\\
  \ADefine{
    \Operators_{
      \MkArity{}{\SortExp}
    }
  }{
    \mathbf{S}_\SortExp
  }\\
  \ADefine{
    \Operators_{
      \MkArity{
        \MkValence{}{}{\SortExp}
      }{
        \SortExp
      }
    }
  }{
    \mathbf{S}_\SortExp
  }
\end{align*}
